Supplemental Materials: \emph{Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours}

### 2015-03-13 Publications/2015-NeuroImage/08-acknowledgements.tex
modify font, add lineno
fix acks

\section*{Acknowledgment}
The authors thank V. Estellers for early discussions at the beginning of this project,
  and L. Vese for her support during OE's research visits in her laboratory.

This study is supported by: the Spain's Ministry of Science and Innovation
  (projects TEC2010-21619- C04-03, TEC2011-28972-C02-02, CDTI-CENIT
  AMIT and INNPACTO PRECISION), Comunidad de Madrid (ARTEMIS) and
  European Regional Development Funds; the Center for Biomedical Imaging
  (CIBM) of the Geneva and Lausanne Universities and the EPFL, as well as the
  Leenaards and Louis Jeantet foundations.
DZ is supported by the Swiss National Science Foundation (SNF) under grant PBELP2-137727.

>>>>

\section*{Acknowledgments}
The authors thank V. Estellers for early discussions at the beginning of this project,
  and L. A. Vese for her support during OE's research visits in her laboratory.
We also thank A. Leemans for kindly sharing a p-code version of \emph{ExploreDTI} from
  which settings for \emph{elastix} could be extracted.

DZ is supported by the Swiss National Science Foundation under grant PBELP2-137727.
This study is supported by: the Spain's Ministry of Science and Innovation
  (projects TEC2013-48251-C2-2-R and INNPACTO XIORT), Comunidad de Madrid (TOPUS) and
  European Regional Development Funds; the Center for Biomedical Imaging
  (CIBM) of the Geneva and Lausanne Universities and the EPFL, as well as the
  Leenaards and Louis Jeantet foundations.
